Introduction to LLL\\``Cryptography''

### 2021-05-27 paper.tex
Fix gauss svp image

If we take for example $v_1 = (10, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
obtain $w_1 = (3, -1), w_2 = (4, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.

@@

Example in \ref{fig:cvp}

>>>>

If we take for example $v_1 = (8, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
obtain $w_1 = (1, -1), w_2 = (6, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.

@@

TODO FIX \ref{fig:cvp} is wrong, the lattice is different.
